%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Consultant Engineer} % Job title
    {Siemens Process Systems Engineering (formerly "Process Systems Enterprise")} % Organization
    {London, UK} % Location
    {Jan. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Configure,test and deliver Digital application solutions based on gPROMS for clients}
        \item {Responsible for real time optimization projects, using digital twins}
        \item {Responsible for Spray Dryer digital twin solutions}
        \item {Head of data processing development}
        \item {Currently on a part time with DevOps teams to set up CI/CD pipelines for the Digital Applications teams}
        \item {HMI deployment to monitor process KPIs}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Automation Engineer} % Job title
    {Gavieiro Automação} % Organization
    {Sete Casas, Loures, Portugal} % Location
    {Nov. 2019 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Configuration, validation, deployment and testing of DeltaV DCS automation modules, complying to GMP standards in pharmaceutical industry.}
        \item {Worked for Hovione, at Sete Casas plant}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {IFP Energies Nouvelles} % Organization
    {Lyon, France} % Location
    {Mar. 2016 - Exp. Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {"Benchmarking of internal modelling tools using industrial data follow up", working on my Master Thesis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {Intercement} % Organization
    {Alhandra, Portugal} % Location
    {Jul. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Testing of adjuvants in Portland cement production.}
        \item {Implemented a distributed web stress test tool with high anonymity.}
        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
      \end{cvitems}
    }

\end{cventries}
