%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Consultant Engineer} % Role
    {Natural gas network optimization} % OProject name
    {Middle East} % Location
    {Jan. 2021 - Sep 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Objective: Simulate and optimize in real time the entire national production network for natural gas. }
        \item {Use of digital twins of several plants and pipelines, on a network, with an HMI that allows the user to read recommendations updated periodically from the advisor,run "what-if" scenarios and generate reports. }
        \item {Deployment of data processing tools, as the application must automatically filter bad data.}
        \item {Challenging deployment due to strict cybersecurity requirements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant Engineer} % Role
    {Spray Dryer soft sensor} % OProject name
    {Netherlands} % Location
    {Aug. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Objective: Deploy a soft sensing app  in a spray dryer. }
        \item {Use of a digital twins of a spray dryer, on an open loop, with an HMI that allows the user to read soft sensed data on the product being dried }
       \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Consultant Engineer} % Role
    {Data processing development group} % OProject name
    {London} % Location
    {Jan. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Objective: Improve data processing workflows }
        \item {Continued development of a user friendly Python based data processing tool that quickly allows the user to visualize and test data processing logics on a dataset. }
        \item {The deployment of this tool in the company helped modellers and consultants filter and visualize test data faster, as it was possible to quickly test and visualize how the data reacts to the processing logics allowed by the application. }
       \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
